%کلمات کلیدی انگلیسی
\latinkeywords{Mobie Robots, Quadrupedal Robot, Legged Robot, SolidWorks, Algorithm, Microcontroller}
%چکیده انگلیسی

\en-abstract{
In today's world, robots play a significant role in human life. Mobile robots, due to their interaction with the environment, differ from other machines. They can create changes in their surroundings based on their actions and respond to the world around them. The diverse applications of robots in simplifying human life have led engineers to pay special attention to robots.
\\
Among all mobile robots, quadruped robots are a type of legged robot that, due to their ability to explore all types of terrains like humans and animals, outperform wheeled robots. The advantage of quadruped robots is that they maintain their stability when standing still and require control when walking.
\\
In this thesis, we first introduced robots, their types, with a focus on constructed quadruped robots, and their applications. Then, we delved into the discussion of designing a model and building a robot using SolidWorks software. In this design process, an initial model was created, and efforts were made to improve its performance after addressing its flaws, resulting in a refined final version. Subsequently, we discussed the hardware and components used in the robot, including motors, microcontrollers, and various modules. Finally, we described the algorithms used and the programming on the robot's microcontroller. 
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
	\begin{flushleft}
	\section*{\LARGE\centering Abstract}

	\een-abstract

	\vspace*{.5cm}
	{\large\textbf{Key Words:}}\par
	\vspace*{.5cm}
	\elatinkeywords
	\end{flushleft}
\end{latin}